\documentclass[10pt]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=*,noitemsep,topsep=0pt}
\usepackage[hidelinks]{hyperref}
\pagenumbering{gobble}
\linespread{1.1}

\begin{document}

\begin{center}
    {\LARGE \textbf{ Rohan Mehta }} \\[2pt]
    \href{mailto:rohan.mehta@gmail.com}{rohan.mehta@gmail.com} \,|\, +91-9876543210 \,|\, 
    \href{https://linkedin.com/in/rohanmehta}{https://linkedin.com/in/rohanmehta} \,|\, 
    \href{https://github.com/rohanmehta}{https://github.com/rohanmehta}
\end{center}
\vspace{4pt}
\section*{Education} \begin{itemize} \item B.Tech in Computer Science, IIT Delhi, 2020 - 2024, CGPA: 8.6/10 \end{itemize}\section*{Skills} \begin{itemize} \item \textbf{Languages}: Python, Java, JavaScript, SQL, MongoDB \item \textbf{Frameworks}: React.js, Node.js, Spring Boot \item \textbf{Other}: Machine Learning, System Design, Data Structures \& Algorithms \end{itemize}\section*{Experience} \textbf{Software Engineering Intern, Infosys} \hfill May 2023 - July 2023 \begin{itemize} \item Designed and integrated REST APIs for client applications. \item Optimized SQL queries with a 20 percent improvement in performance. \item Collaborated with senior engineers to implement coding best practices. \end{itemize} \textbf{Backend Developer Intern, PayPal} \hfill Jan 2024 - June 2024 \begin{itemize} \item Built scalable microservices using Spring Boot and Docker for payment workflows. \item Implemented Redis caching, improving transaction processing speed by 35 percent. \item Enhanced fraud detection algorithms by integrating ML models into real-time pipelines. \item Worked closely with global PayPal engineering teams on distributed systems at scale. \end{itemize}\section*{Projects} \textbf{AlgoAnims - Algorithm Visualizer} \begin{itemize} \item Built an interactive platform using React and Express to visualize sorting, graph, and search algorithms with step-by-step animations. \item \url{https://github.com/rohanmehta/algoanims} \end{itemize} \textbf{Realtime Chat App} \begin{itemize} \item Implemented a secure chat application with WebSockets, JWT authentication, and scalable backend using Spring Boot and Redis. \item \url{https://github.com/rohanmehta/realtime-chat} \end{itemize}\section*{Additional} \begin{itemize} \item Winner, Smart India Hackathon 2023 \item LeetCode Rating: 2000+ (Top 5 percent) \item Organized 'Winter Tech Break' workshop on scalable systems (Kafka, Redis, Load Balancing). \end{itemize}\end{document}